A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-07-19 paper/elsarticle/elsarticle-template.tex
paper

\usepackage{lineno,hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{colortbl}
\modulolinenumbers[5]

@@

We propose a spatial AR system for augmenting planar scene surfaces that produces the effect of keystone correction analytically. Our system does so in a manner that facilitates placement of augmentations in the scene by enabling intuitively (i) placing the desired augmentations in accordance with the axes of an image of the scene acquired by a camera placed to face downwards towards the scene plane, and (ii) reasoning about the desired dimensions of the projected augmentations in metric terms. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling wide-area factory floor augmentation exceeding the bounds of the projector's immediate field of view.
\end{abstract}

@@

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity, hence alternatively termed a `colineation'---and is ultimately the approach we take as well. The intuition for why a transformation that maps lines to lines can serve to model the appropriate image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines would give the desired effect.

@@

In practice, calibrating a camera relies on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output the calibration matrix~$\mathtt{K}$, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. To calibrate a camera, a calibration surface such as a chessboard pattern is used to identify the correspondences. Calibration of a projector can be carried out in precisely the same manner insofar as step (ii) is concerned; the major difference in projector calibration relative to the calibrating a camera concerns the manner in which 2D-3D correspondences are identified, i.e., between pixels in the image plane of the projector and the corresponding points in the scene. A convenient consequence of the approach we take to identifying the 3D points of the 2D-3D correspondences needed for projector calibration is, for each target location, recovery of the pose (i.e., position and orientation) of (i) the projector and of (ii) the scene plane, both relative to the coordinate frame of the camera.

\paragraph{Camera calibration} We recover 2D-3D correspondences in support of calibrating the downwards-facing camera is carried out by relying on a planar calibration surface to automatically identify correspondences between the 3D points on the calibration surface and their 2D correspondences in the image plane. The classical calibration surface is a chessboard pattern. The 3D corner points of the chessboard are obtained \textit{a priori} in a coordinate system defined in the plane of the chessboard\footnote{E.g., $(0,0,0), (1.5,0,0), (3,0,0), \dots, (9,7.5,0)$ for a chessboard with $7~\times{}~6$ corners ($8~\times{}~7$ squares), with each square of length and width of 1.5 unit, respectively. Note that the units of the chessboard's 3D points give the units of the camera calibration, and---owing to how our projector calibration relies on the camera calibration---of the projector calibration as well.}, requiring knowledge only of the dimensions of the chessboard pattern and of the length of a side of a chessboard square. The corresponding 2D points are obtained, in the same order, using a specialized algorithm \cite{bradski2000opencv}. A set of calibration images is acquired, each with the calibration pattern visible in a different part of the image plane, and such that the center and all corners and edges of the image plane are covered, the camera's autofocus setting be off, and the camera's zoom factor remain fixed. 2D-3D correspondences are then recovered for each calibration image, and the resulting list is passed on as input to an optimization procedure that relies on bundle adjustment to yield the camera calibration matrix~$\mathtt{K}_\text{cam}$ and the associated lens distortion model coefficients.

@@

\begin{figure}
    \centering
    \subfloat[\centering Oblique view.]{{\includegraphics[height=4.2cm]{images/1.pdf}}}
    \qquad
    \subfloat[\centering Downwards view.]{{\includegraphics[height=4.2cm]{images/3_above3.png}}}
    \caption{The virtual camera is obtained by (i) rotating the camera (top left, black) about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. The virtual projector is obtained by (ii) rotating the projector (bottom left, black) about the point of intersection of its optical axis with the scene plane such that the optical axis be made parallel with the scene plane's normal vector, (iii) rotating the $X$- and $Y$-axes to align them with those of the virtual camera, and (iv) translating along the normal direction to achieve the desired projected image dimensions in metric units.} %The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera.
    \label{fig:virtualproj}
\end{figure}

>>>>

\usepackage{lineno,hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{amsmath}
\modulolinenumbers[5]

@@

We propose a spatial AR system for augmenting planar scene surfaces that produces the effect of keystone correction analytically. Our system renders the placement of augmentations in the scene intuitive in two ways. First, (i) placement of the desired augmentations is carried out in accordance with the axes of an image of the scene acquired by a camera placed to face downwards towards the scene plane; second, (ii) the desired dimensions of the projected augmentations is given in metric terms. Moreover, our system is able to handle projector equipped with a steerable mirror, enabling wide-area factory floor augmentation exceeding the bounds of a single projector's immediate field~of~view.
\end{abstract}

@@

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity, hence alternatively termed a `colineation'---and is ultimately the approach we take as well. The intuition for why it is that a transformation that maps lines to lines can serve to model the appropriate image warp can be drawn from considering a planar chessboard pattern: looking at an image of a chessboard acquired from an oblique angle, one observes that lines parallel in the chessboard appear to meet in respective vanishing points; looking at an image of the same chessboard acquired frontally with respect to the plane of the chessboard, lines parallel in the chessboard appear parallel in the image (i.e., they are said to meet `at infinity'). To warp the former image (where lines parallel in the scene meet in respective vanishing points) such that the lines of the chessboard appear as in the latter image (where lines parallel in the scene meet at infinity), a transformation that maps lines to lines would be sufficient.

@@

In practice, calibrating a camera relies on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output the calibration matrix~$\mathtt{K}$, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D points \cite{Hartley2004,zhang2000flexible}. To calibrate a camera, images of a calibration surface such as a chessboard pattern are used to identify the 2D-3D correspondences $\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_i\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, and $n_\text{im}$ the number of such images. Bundle adjustment is used to obtain the calibration matrix~$\mathtt{K}$ and rigid body transformations $g = (\mathtt{R}_j, \mathbf{t}_j) \in SE(3)$ that minimize the reprojection error
\begin{equation}
\sum_{i,j} d\big(\mathbf{x}_{i,j}, \mathtt{K}(\mathtt{R}_j\mathbf{X}_i + \mathbf{t}_j)\big),
\label{re}
\end{equation}
where $\mathbf{X}_{i,j} = \mathtt{R}_j\mathbf{X}_i + \mathbf{t}_j$ expresses $\mathbf{X}_i$ in the camera coordinate frame corresponding to the $j^{\text{th}}$ calibration image, $\mathtt{K}\mathbf{X}_{i,j} \in \mathbb{R}^2$ gives the projection of $\mathbf{X}_i$ to that image, and $d$ is a distance function. The inverse rigid body transformation~$g^{-1}$ gives the pose of the $j^{\text{th}}$ camera relative to the points $\{\mathbf{X}_i\}$.

Calibration of a projector can be carried out in precisely the same manner insofar as step (ii) is concerned; the major difference in projector calibration relative to the calibrating a camera concerns the manner in which 2D-3D correspondences are identified, i.e., between pixels in the image plane of the projector and the corresponding points in the scene. A convenient consequence of the approach we take to identifying the 3D points of the 2D-3D correspondences needed for projector calibration is, for each target location, recovery of the pose (i.e., position and orientation) of (i) the projector and of (ii) the scene plane, both relative to the coordinate frame of the camera.

\paragraph{Camera calibration} We recover 2D-3D correspondences in support of calibrating the downwards-facing camera by relying on a planar calibration surface to automatically identify correspondences between the 3D points on the calibration surface and their 2D correspondences in the image plane. The classical calibration surface is a chessboard pattern. The 3D corner points of the chessboard are obtained \textit{a priori} in a coordinate system defined in the plane of the chessboard\footnote{E.g., $(0,0,0), (1.5,0,0), (3,0,0), \dots, (9,7.5,0)$ for a chessboard with $7~\times{}~6$ corners ($8~\times{}~7$ squares), with each square of length and width of 1.5 unit, respectively. Note that the units of the chessboard's 3D points give the units of the camera calibration, and---owing to how our projector calibration relies on the camera calibration---of the projector calibration as well.}, requiring knowledge only of the dimensions of the chessboard pattern and of the length of a side of a chessboard square. The corresponding 2D points are obtained, in the same order, using a specialized algorithm \cite{bradski2000opencv}. A set of calibration images is acquired, each with the calibration pattern visible in a different part of the image plane, and such that the center and all corners and edges of the image plane are covered, the camera's autofocus setting be off, and the camera's zoom factor remain fixed. 2D-3D correspondences are then recovered for each calibration image, and the resulting list is passed on as input to an optimization procedure that relies on bundle adjustment to yield the camera calibration matrix~$\mathtt{K}_\text{cam}$ and the associated lens distortion model coefficients.

@@

\begin{figure}
    \centering
    \subfloat[\centering Oblique view.]{{\includegraphics[height=4.2cm]{images/1.pdf}}}
    \qquad
    \subfloat[\centering Downwards view.]{{\includegraphics[height=4.2cm]{images/3_above3.png}}}
    \caption{The virtual camera is obtained by (i) rotating the camera (top left, black) about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. The virtual projector is obtained by (ii) rotating the projector (bottom left, black) about the point of intersection of its optical axis with the scene plane such that the optical axis be made parallel with the scene plane's normal vector, (iii) rotating the $X$- and $Y$-axes to align them with those of the virtual camera, and (iv) translating along the normal direction to achieve the desired metric projected image dimensions.} %The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera.
    \label{fig:virtualproj}
\end{figure}
